Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review (Supplementary Files)

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Removed wordstyle document

---
title: "Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review (Supplementary Files)"
author: "James Azam"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  word_document:
    keep_md: yes
    reference_docx: word-style.docx
    toc: yes
---

>>>>

---
title: "Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review (Supplementary Files)"
author: "James Azam"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  word_document:
    keep_md: yes
    toc: yes
---
